---
title: "R2_partitioning"
author: "Christopher"
date: "2026-05-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### load packages

```{r}

```

#### load data

```{r}
data <- read.csv("data_with_stopwords.csv")
```

#### prepare data for models

```{r}
#### simple coding for categorical predictors:
## code recommended by Figner et al. (2024) to set zero-to-sum contrast:
options(contrasts = c("contr.sum", "contr.poly"))

## making sure they are factors:
data$recording_location <- as.factor(data$recording_location)
data$colour <- as.factor(data$colour)

#### mean centering of continuous variables:
## groups the variables that should be mean centered:
predictors_to_be_centered <- c("GPT_FAM", 
                               "GPT_val",
                               "GPT_arou",
                               "GPT_concr",
                               "GPT_AoA_ft",
                               "age",
                               "reading_speed",
                               "word_length_single",
                               "previous_reading_times_log",
                               "compr_Qs_percent_correct",
                               "surprisal_2_words_context",
                               "entropy_2_words_context",
                               "zipf_frequency")

## performs the mean centering:
data[paste0(predictors_to_be_centered, "_centered")] <- lapply(data[predictors_to_be_centered], 
                                                      function(x) as.vector(scale(x, 
                                                                                  center = TRUE, 
                                                                                  scale = FALSE)))

#### selecting relevant columns from data to create model_data:
model_data <- data %>% select(word, ID, text_nr, recording_location, block_nr, trial_nr, word_single, GPT_FAM_centered, GPT_concr_centered, GPT_val_centered, GPT_arou_centered, GPT_AoA_ft_centered, age_centered, word_length_single_centered, previous_reading_times_log_centered, compr_Qs_percent_correct_centered, surprisal_2_words_context_centered, entropy_2_words_context_centered, zipf_frequency_centered, duration)

#### calculating the interaction terms:
model_data$familiarity_interaction <- model_data$GPT_FAM_centered * model_data$age_centered
model_data$concreteness_interaction <- model_data$GPT_concr_centered * model_data$age_centered
model_data$valence_interaction <- model_data$GPT_val_centered * model_data$age_centered
model_data$arousal_interaction <- model_data$GPT_arou_centered * model_data$age_centered
model_data$aoa_interaction <- model_data$GPT_AoA_ft_centered * model_data$age_centered
model_data$surprisal_interaction <- model_data$surprisal_2_words_context_centered * model_data$age_centered
model_data$entropy_interaction <- model_data$entropy_2_words_context_centered * model_data$age_centered
model_data$frequency_interaction <- model_data$zipf_frequency_centered * model_data$age_centered
```

#### models for research question I

```{r}
#### Research Question: Which of the five GPTs (fam, concr, val, arou, aoa) accounts for most variance? Hypothesis: fam
#### We create one large model containing all five GPTs, and five individual models each containing only one of the five.

#### large model:
complete_model_hypothesis_I <- lmer(log(duration) ~ 
                                      GPT_FAM_centered +
                                      GPT_concr_centered +
                                      GPT_val_centered +
                                      GPT_arou_centered +
                                      GPT_AoA_ft_centered +
                                      recording_location +
                                      age_centered +
                                      word_length_single_centered +
                                      block_nr +
                                      trial_nr +
                                      (1|ID) +
                                      (1|text_nr),
                                      data = model_data,
                                      REML = TRUE,
                                      lmerControl(optimizer = "bobyqa"))


#### individual models:
# familiarity-only model
individual_model_hypothesis_I_familiarity <- lmer(log(duration) ~ GPT_FAM_centered + recording_location + age_centered + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))

# concreteness-only model
individual_model_hypothesis_I_concreteness <- lmer(log(duration) ~ GPT_concr_centered + recording_location + age_centered + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))

# valence-only model
individual_model_hypothesis_I_valence <- lmer(log(duration) ~ GPT_val_centered + recording_location + age_centered + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))

# arousal-only model
individual_model_hypothesis_I_arousal <- lmer(log(duration) ~ GPT_arou_centered + recording_location + age_centered + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))

# age-of-acquisition-only model
individual_model_hypothesis_I_aoa <- lmer(log(duration) ~ GPT_AoA_ft_centered + recording_location + age_centered + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))
```

#### partitioning of variance for research question I

```{r}
#### We use PartR2 to calculate the part R2 and inclusive R2.


## complete model
complete_model_hypothesis_I_partR2 <- partR2(complete_model_hypothesis_I, partvars = c("GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


# familiarity-only model
individual_model_hypothesis_I_familiarity_partR2 <- partR2(individual_model_hypothesis_I_familiarity, partvars = c("GPT_FAM_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


# concreteness-only model
individual_model_hypothesis_I_concreteness_partR2 <- partR2(individual_model_hypothesis_I_concreteness, partvars = c("GPT_concr_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


# valence-only model
individual_model_hypothesis_I_valence_partR2 <- partR2(individual_model_hypothesis_I_valence, partvars = c("GPT_val_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


# arousal-only model
individual_model_hypothesis_I_arousal_partR2 <- partR2(individual_model_hypothesis_I_arousal, partvars = c("GPT_arou_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


# age-of-acquisiton model
individual_model_hypothesis_I_aoa_partR2 <- partR2(individual_model_hypothesis_I_aoa, partvars = c("GPT_AoA_ft_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


#### We use glmm.hp to calculate the individual marginal R2.


## complete model
complete_model_hypothesis_I_glmm_hp<- glmm.hp(complete_model_hypothesis_I) 

## familiarity-only model
individual_model_hypothesis_I_familiarity_glmm_hp <- glmm.hp(individual_model_hypothesis_I_familiarity)

## concreteness-only model
individual_model_hypothesis_I_concreteness_glmm_hp <- glmm.hp(individual_model_hypothesis_I_concreteness)

## valence_only model
individual_model_hypothesis_I_valence_glmm_hp <- glmm.hp(individual_model_hypothesis_I_valence)

## arousal-only model
individual_model_hypothesis_I_arousal_glmm_hp <- glmm.hp(individual_model_hypothesis_I_arousal)

## age-of-acqisition-only model
individual_model_hypothesis_I_aoa_glmm_hp <- glmm.hp(individual_model_hypothesis_I_aoa)
```

#### table overview for research question I 

```{r}
#### table research question I
table_hypothesis_I <- data.frame(
  "Predictor" = c("Familiarity", "Concreteness", "Valence", "Arousal", "Age-of-Acquisition"),
  "Part R2" = c(complete_model_hypothesis_I_partR2$R2$estimate[2:6]),
  "Individual Marginal R2" = c(complete_model_hypothesis_I_glmm_hp$hierarchical.partitioning[1:5,3]),
    "Part R2_ind" = c(individual_model_hypothesis_I_familiarity_partR2$R2$estimate[2], individual_model_hypothesis_I_concreteness_partR2$R2$estimate[2], individual_model_hypothesis_I_valence_partR2$R2$estimate[2], individual_model_hypothesis_I_arousal_partR2$R2$estimate[2], individual_model_hypothesis_I_aoa_partR2$R2$estimate[2]),
 "Individual Marginal R2_ind" = c(individual_model_hypothesis_I_familiarity_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_I_concreteness_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_I_valence_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_I_arousal_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_I_aoa_glmm_hp$hierarchical.partitioning[1, 3]),
  "Inclusive R2_ind" = c(individual_model_hypothesis_I_familiarity_partR2$IR2$estimate[1], individual_model_hypothesis_I_concreteness_partR2$IR2$estimate[1], individual_model_hypothesis_I_valence_partR2$IR2$estimate[1], individual_model_hypothesis_I_arousal_partR2$IR2$estimate[1], individual_model_hypothesis_I_aoa_partR2$IR2$estimate[1]))


#### selecting how many digits the nice_table showcases
fun <- function(x) {formatC(x, format = "f", digits = 4)} # tables should only show 4 decimals

#### setting up the nice_table
table_hypothesis_one <- nice_table(
  table_hypothesis_I,
  col.format.custom = 1:7,
  format.custom = "fun")


#### additional head columns
table_hypothesis_one <- table_hypothesis_one |>
  set_header_labels(
    Part.R2 = "Part R2",
    Individual.Marginal.R2 = "Individual Marginal R2",
    Inclusive.R2 = "Inclusive R2",
    Part.R2_ind = "Part R2",
    Individual.Marginal.R2_ind = "Individual Marginal R2",
    Inclusive.R2_ind = "Inclusive R2") |>
  add_header_row(top = TRUE, values = c("","Complete Model",
                                        "Individual Models", ""),colwidths = c(1,2,2,1))
print(table_hypothesis_one)
#save_as_image(table_hypothesis_one, path = "table_hypothesis_one.png")
```

#### models for hypothesis II

```{r}
#### complete model containing the GPTs, surprisal, entropy, and freqeuncy:
complete_model_hypothesis_II <- lmer(log(duration) ~ 
                                      GPT_FAM_centered +
                                      GPT_concr_centered +
                                      GPT_val_centered +
                                      GPT_arou_centered +
                                      GPT_AoA_ft_centered +
                                      surprisal_2_words_context_centered +
                                      entropy_2_words_context_centered +
                                      zipf_frequency_centered +
                                      recording_location +
                                      age_centered +
                                      word_length_single_centered +
                                      block_nr +
                                      trial_nr +
                                      (1|ID) +
                                      (1|text_nr),
                                      data = model_data,
                                      REML = TRUE,
                                      lmerControl(optimizer = "bobyqa"))

#### individual models:
# for suprisal-only model
individual_model_hypothesis_II_surprisal <- lmer(log(duration) ~ surprisal_2_words_context_centered + recording_location + age_centered + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))

# for entropy-only model
individual_model_hypothesis_II_entropy <- lmer(log(duration) ~ entropy_2_words_context_centered + recording_location + age_centered + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))

# for frequency-only model
individual_model_hypothesis_II_frequency <- lmer(log(duration) ~ zipf_frequency_centered + recording_location + age_centered + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))

```

#### partitioning of variance for research question II

```{r}
#### We use PartR2 to calculate the part R2 and inclusive R2.

## complete model
complete_model_hypothesis_II_partR2 <- partR2(complete_model_hypothesis_II, partvars = c("GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1) 


## surprisal-only model
individual_model_hypothesis_II_surprisal_partR2 <- partR2(individual_model_hypothesis_II_surprisal, partvars = c("surprisal_2_words_context_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


## entropy-only model
individual_model_hypothesis_II_entropy_partR2 <- partR2(individual_model_hypothesis_II_entropy, partvars = c("entropy_2_words_context_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


## frequency-only model
individual_model_hypothesis_II_frequency_partR2 <- partR2(individual_model_hypothesis_II_frequency, partvars = c("zipf_frequency_centered", "recording_location", "age_centered", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", CI = 0.95, nboot = 25, max_level = 1)


#### We use glmm.hp to calculate the individual marginal R2.


## complete model
complete_model_hypothesis_II_glmm_hp <- glmm.hp(complete_model_hypothesis_II)

## surprisal-only model
individual_model_hypothesis_II_surprisal_glmm_hp <- glmm.hp(individual_model_hypothesis_II_surprisal)

## entropy-only model
individual_model_hypothesis_II_entropy_glmm_hp <- glmm.hp(individual_model_hypothesis_II_entropy)

## frequency-only model
individual_model_hypothesis_II_frequency_glmm_hp <- glmm.hp(individual_model_hypothesis_II_frequency)
```

#### table research question II

```{r}
table_hypothesis_II <- data.frame(
  "Predictor" = c("Familiarity", "Concreteness", "Valence", "Arousal", "Age-of-Acquisition", "Surprisal", "Entropy", "Frequency"),
  "Part R2" = c(complete_model_hypothesis_II_partR2$R2$estimate[2:9]),
  "Individual Marginal R2" = c(complete_model_hypothesis_II_glmm_hp$hierarchical.partitioning[1:8, "Individual"]),
    "Part R2_ind" = c(individual_model_hypothesis_I_familiarity_partR2$R2$estimate[2], individual_model_hypothesis_I_concreteness_partR2$R2$estimate[2], individual_model_hypothesis_I_valence_partR2$R2$estimate[2], individual_model_hypothesis_I_arousal_partR2$R2$estimate[2], individual_model_hypothesis_I_aoa_partR2$R2$estimate[2], individual_model_hypothesis_II_surprisal_partR2$R2$estimate[2], individual_model_hypothesis_II_entropy_partR2$R2$estimate[2], individual_model_hypothesis_II_frequency_partR2$R2$estimate[2]),
    "Individual Marginal R2_ind" = c(individual_model_hypothesis_I_familiarity_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_I_concreteness_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_I_valence_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_I_arousal_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_I_aoa_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_II_surprisal_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_II_entropy_glmm_hp$hierarchical.partitioning[1, 3], individual_model_hypothesis_II_frequency_glmm_hp$hierarchical.partitioning[1, 3]),
  "Inclusive R2_ind" = c(individual_model_hypothesis_I_familiarity_partR2$IR2$estimate[1], individual_model_hypothesis_I_concreteness_partR2$IR2$estimate[1], individual_model_hypothesis_I_valence_partR2$IR2$estimate[1], individual_model_hypothesis_I_arousal_partR2$IR2$estimate[1], individual_model_hypothesis_I_aoa_partR2$IR2$estimate[1], individual_model_hypothesis_II_surprisal_partR2$IR2$estimate[1], individual_model_hypothesis_II_entropy_partR2$IR2$estimate[1], individual_model_hypothesis_II_frequency_partR2$IR2$estimate[1]))


#### selecting how many digits the nice_table showcases
fun <- function(x) {formatC(x, format = "f", digits = 4)} # tables should only show 4 decimals

#### setting up the nice_table
table_hypothesis_two <- nice_table(
  table_hypothesis_II,
  col.format.custom = 1:9,
  format.custom = "fun")


#### additional head columns
table_hypothesis_two <- table_hypothesis_two |>
  set_header_labels(
    Part.R2 = "Part R2",
    Individual.Marginal.R2 = "Individual Marginal R2",
    Inclusive.R2 = "Inclusive R2",
    Part.R2_ind = "Part R2",
    Individual.Marginal.R2_ind = "Individual Marginal R2",
    Inclusive.R2_ind = "Inclusive R2") |>
  add_header_row(top = TRUE, values = c("","Complete Model",
                                        "Individual Models", ""),colwidths = c(1,2,2,1))
print(table_hypothesis_two)
#save_as_image(table_hypothesis_two, path = "table_hypothesis_two.png")
```

#### models for research question III

```{r}
#### first set of models: individual models with only one term and its interaction + baseline fixed and random effects


# familiarity-only model without controlling for other key predictors
individual_model_hypothesis_III_familiarity_interaction <- lmer(log(duration) ~ familiarity_interaction + GPT_FAM_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# concreteness-only model without controlling for other key predictors
individual_model_hypothesis_III_concreteness_interaction <- lmer(log(duration) ~ concreteness_interaction + GPT_concr_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# valence-only model without without controlling for other key predictors
individual_model_hypothesis_III_valence_interaction <- lmer(log(duration) ~ valence_interaction + GPT_val_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# arousal-only model without controlling for other key predictors
individual_model_hypothesis_III_arousal_interaction <- lmer(log(duration) ~ arousal_interaction + GPT_arou_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# age-of-acquisition-only model without controlling for other key predictors
individual_model_hypothesis_III_aoa_interaction <- lmer(log(duration) ~ aoa_interaction + GPT_AoA_ft_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# surprisal-only model without controlling for other key predictors
individual_model_hypothesis_III_surprisal_interaction <- lmer(log(duration) ~ surprisal_interaction + surprisal_2_words_context_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# entropy-only model without controlling for other key predictors
individual_model_hypothesis_III_entropy_interaction <- lmer(log(duration) ~ entropy_interaction + entropy_2_words_context_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# frequency-only model without controlling for other key predictors
individual_model_hypothesis_III_frequency_interaction <- lmer(log(duration) ~ frequency_interaction + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


#### second set of models: additionally the other fixed effects


# familiarity model with control for other key predictors
model_III_fam_int <- lmer(log(duration) ~ familiarity_interaction + GPT_FAM_centered + GPT_concr_centered + GPT_val_centered + GPT_arou_centered + GPT_AoA_ft_centered + surprisal_2_words_context_centered + entropy_2_words_context_centered + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# concreteness model with control for other key predictors
model_III_concr_int <- lmer(log(duration) ~ concreteness_interaction + GPT_FAM_centered + GPT_concr_centered + GPT_val_centered + GPT_arou_centered + GPT_AoA_ft_centered + surprisal_2_words_context_centered + entropy_2_words_context_centered + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# valence model with control for other key predictors
model_III_val_int <- lmer(log(duration) ~ valence_interaction + GPT_FAM_centered + GPT_concr_centered + GPT_val_centered + GPT_arou_centered + GPT_AoA_ft_centered + surprisal_2_words_context_centered + entropy_2_words_context_centered + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# arousal model with control for other key predictors
model_III_arou_int <- lmer(log(duration) ~ arousal_interaction + GPT_FAM_centered + GPT_concr_centered + GPT_val_centered + GPT_arou_centered + GPT_AoA_ft_centered + surprisal_2_words_context_centered + entropy_2_words_context_centered + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# age-of-acquisition model with control for other key predictors
model_III_aoa_int <- lmer(log(duration) ~ aoa_interaction + GPT_FAM_centered + GPT_concr_centered + GPT_val_centered + GPT_arou_centered + GPT_AoA_ft_centered + surprisal_2_words_context_centered + entropy_2_words_context_centered + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# surprisal model with control for other key predictors
model_III_sur_int <- lmer(log(duration) ~ surprisal_interaction + GPT_FAM_centered + GPT_concr_centered + GPT_val_centered + GPT_arou_centered + GPT_AoA_ft_centered + surprisal_2_words_context_centered + entropy_2_words_context_centered + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# entropy model with control for other key predictors
model_III_ent_int <- lmer(log(duration) ~ entropy_interaction + GPT_FAM_centered + GPT_concr_centered + GPT_val_centered + GPT_arou_centered + GPT_AoA_ft_centered + surprisal_2_words_context_centered + entropy_2_words_context_centered + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))


# frequency model with control for other key predictors
model_III_fre_int <- lmer(log(duration) ~ frequency_interaction + GPT_FAM_centered + GPT_concr_centered + GPT_val_centered + GPT_arou_centered + GPT_AoA_ft_centered + surprisal_2_words_context_centered + entropy_2_words_context_centered + zipf_frequency_centered + age_centered + recording_location + word_length_single_centered + block_nr + trial_nr + (1|ID) + (1|text_nr), data = model_data, REML = TRUE, lmerControl(optimizer = "bobyqa"))
```

#### partitioning of variance for research question III for first set of (smaller) models:

```{r}
#### We use PartR2 to calculate the part R2 and inclusive R2.
#### individual models:


## familiarity-only model
individual_model_hypothesis_III_familiarity_interaction_partR2 <- partR2(individual_model_hypothesis_III_familiarity_interaction, partvars = c("familiarity_interaction", "GPT_FAM_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## concreteness-only model
individual_model_hypothesis_III_concreteness_interaction_partR2 <- partR2(individual_model_hypothesis_III_concreteness_interaction, partvars = c("concreteness_interaction", "GPT_concr_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## valence-only model
individual_model_hypothesis_III_valence_interaction_partR2 <- partR2(individual_model_hypothesis_III_valence_interaction, partvars = c("valence_interaction", "GPT_val_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## arousal-only model
individual_model_hypothesis_III_arousal_interaction_partR2 <- partR2(individual_model_hypothesis_III_arousal_interaction, partvars = c("arousal_interaction", "GPT_arou_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## age-of-acquisition-only model
individual_model_hypothesis_III_aoa_interaction_partR2 <- partR2(individual_model_hypothesis_III_aoa_interaction, partvars = c("aoa_interaction", "GPT_AoA_ft_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## surprisal-only model
individual_model_hypothesis_III_surprisal_interaction_partR2 <- partR2(individual_model_hypothesis_III_surprisal_interaction, partvars = c("surprisal_interaction", "surprisal_2_words_context_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## entropy-only model
individual_model_hypothesis_III_entropy_interaction_partR2 <- partR2(individual_model_hypothesis_III_entropy_interaction, partvars = c("entropy_interaction", "entropy_2_words_context_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## frequency-only model
individual_model_hypothesis_III_frequency_interaction_partR2 <- partR2(individual_model_hypothesis_III_frequency_interaction, partvars = c("frequency_interaction", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


#### glmm.hp for individual marginal R2


# familiarity-only model
individual_model_hypothesis_III_familiarity_interaction_glmm_hp <- glmm.hp(individual_model_hypothesis_III_familiarity_interaction)
# concreteness-only model
individual_model_hypothesis_III_concreteness_interaction_glmm_hp <- glmm.hp(individual_model_hypothesis_III_concreteness_interaction)
# valence-only model
individual_model_hypothesis_III_valence_interaction_glmm_hp <- glmm.hp(individual_model_hypothesis_III_valence_interaction)
# arousal-only model
individual_model_hypothesis_III_arousal_interaction_glmm_hp <- glmm.hp(individual_model_hypothesis_III_arousal_interaction)
# age of acquisition-only model
individual_model_hypothesis_III_aoa_interaction_glmm_hp <- glmm.hp(individual_model_hypothesis_III_aoa_interaction)
# surprisal-only model
individual_model_hypothesis_III_surprisal_interaction_glmm_hp <- glmm.hp(individual_model_hypothesis_III_surprisal_interaction)
# entropy-only model
individual_model_hypothesis_III_entropy_interaction_glmm_hp <- glmm.hp(individual_model_hypothesis_III_entropy_interaction) 
# frequency-only model
individual_model_hypothesis_III_frequency_interaction_glmm_hp <- glmm.hp(individual_model_hypothesis_III_frequency_interaction)
```

#### partitioning of variance for research question III for larger models controlling for other key predictors:

```{r}
#### We use PartR2 to calculate the part R2 and inclusive R2.


## familiarity model
model_III_fam_int_partR2 <- partR2(model_III_fam_int, partvars = c("familiarity_interaction", "GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## concreteness model
model_III_concr_int_partR2 <- partR2(model_III_concr_int, partvars = c("concreteness_interaction", "GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## valence model
model_III_val_int_partR2 <- partR2(model_III_val_int, partvars = c("valence_interaction", "GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## arousal model
model_III_arou_int_partR2 <- partR2(model_III_arou_int, partvars = c("arousal_interaction", "GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## age-of-acquisition model
model_III_aoa_int_partR2 <- partR2(model_III_aoa_int, partvars = c("aoa_interaction", "GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## surprisal model
model_III_sur_int_partR2 <- partR2(model_III_sur_int, partvars = c("surprisal_interaction", "GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## entropy model
model_III_ent_int_partR2 <- partR2(model_III_ent_int, partvars = c("entropy_interaction", "GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


## frequency model
model_III_fre_int_partR2 <- partR2(model_III_fre_int, partvars = c("frequency_interaction", "GPT_FAM_centered", "GPT_concr_centered", "GPT_val_centered", "GPT_arou_centered", "GPT_AoA_ft_centered", "surprisal_2_words_context_centered", "entropy_2_words_context_centered", "zipf_frequency_centered", "age_centered", "recording_location", "word_length_single_centered", "block_nr", "trial_nr"), R2_type = "marginal", nboot = 25, CI = 0.95, max_level = 1)


#### glmm.hp for individual marginal R2


# familiarity-only model
model_III_fam_int_glmm_hp <- glmm.hp(model_III_fam_int)
# concreteness-only model
model_III_concr_int_glmm_hp <- glmm.hp(model_III_concr_int)
# valence-only model
model_III_val_int_glmm_hp <- glmm.hp(model_III_val_int)
# arousal-only model
model_III_arou_int_glmm_hp <- glmm.hp(model_III_arou_int)
# age of acquisition-only model
model_III_aoa_int_glmm_hp <- glmm.hp(model_III_aoa_int)
# surprisal-only model
model_III_sur_int_glmm_hp <- glmm.hp(model_III_sur_int)
# entropy-only model
model_III_ent_int_glmm_hp <- glmm.hp(model_III_ent_int) 
# frequency-only model
model_III_fre_int_glmm_hp <- glmm.hp(model_III_fre_int)
```

#### table research question III

```{r}
#### table for individual models
overview_table_hypothesis_III_individual_models <- data.frame(
  "Interaction" = c("Familiarity x Age", "Concreteness x Age", "Valence x Age", "Arousal x Age", "Age of Acquisition x Age", "Surprisal x Age", "Entropy x Age", "Frequency x Age"),
  "Part R2" = c(individual_model_hypothesis_III_familiarity_interaction_partR2$R2$estimate[2], individual_model_hypothesis_III_concreteness_interaction_partR2$R2$estimate[2], individual_model_hypothesis_III_valence_interaction_partR2$R2$estimate[2], individual_model_hypothesis_III_arousal_interaction_partR2$R2$estimate[2], individual_model_hypothesis_III_aoa_interaction_partR2$R2$estimate[2], individual_model_hypothesis_III_surprisal_interaction_partR2$R2$estimate[2], individual_model_hypothesis_III_entropy_interaction_partR2$R2$estimate[2], individual_model_hypothesis_III_frequency_interaction_partR2$R2$estimate[2]),
  "Individual Marginal R2" = c(individual_model_hypothesis_III_familiarity_interaction_glmm_hp$hierarchical.partitioning[1, "Individual"], individual_model_hypothesis_III_concreteness_interaction_glmm_hp$hierarchical.partitioning[1,"Individual"], individual_model_hypothesis_III_valence_interaction_glmm_hp$hierarchical.partitioning[1,"Individual"], individual_model_hypothesis_III_arousal_interaction_glmm_hp$hierarchical.partitioning[1,"Individual"], individual_model_hypothesis_III_aoa_interaction_glmm_hp$hierarchical.partitioning[1,"Individual"], individual_model_hypothesis_III_surprisal_interaction_glmm_hp$hierarchical.partitioning[1,"Individual"], individual_model_hypothesis_III_entropy_interaction_glmm_hp$hierarchical.partitioning[1,"Individual"], individual_model_hypothesis_III_frequency_interaction_glmm_hp$hierarchical.partitioning[1,"Individual"]),
  "Inclusive R2" = c(individual_model_hypothesis_III_familiarity_interaction_partR2$IR2$estimate[1], individual_model_hypothesis_III_concreteness_interaction_partR2$IR2$estimate[1], individual_model_hypothesis_III_valence_interaction_partR2$IR2$estimate[1], individual_model_hypothesis_III_arousal_interaction_partR2$IR2$estimate[1], individual_model_hypothesis_III_aoa_interaction_partR2$IR2$estimate[1], individual_model_hypothesis_III_surprisal_interaction_partR2$IR2$estimate[1], individual_model_hypothesis_III_entropy_interaction_partR2$IR2$estimate[1], individual_model_hypothesis_III_frequency_interaction_partR2$IR2$estimate[1]))

#### nice_table
fun <- function(x) {formatC(x, format = "f", digits = 4)} # tables should only show 4 decimals

#### setting up the nice_table
table_hypothesis_III <- nice_table(
  overview_table_hypothesis_III_individual_models,
  col.format.custom = 1:7,
  format.custom = "fun")


#### additional head columns
table_hypothesis_III <- table_hypothesis_III |>
  set_header_labels(
    Part.R2 = "Part R2",
    Individual.Marginal.R2 = "Individual Marginal R2",
    Inclusive.R2 = "Inclusive R2")

print(table_hypothesis_III) ## until now this table is restricted to the individual models
```


